---
title: "Supporting Data Fest"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

As our event grows we will need more help from the North State Community to put this fabulous event on. 
How can you support DataFest at Chico State?

### Financial Contributions

We welcome financial donations from individuals and businesses. Donations are used to provide food, supplies, event t-shirts, caffeine and prizes. 

```{r}
# fundraising objective
z <- 2500
# amount gathered
y <- 200 

library(RColorBrewer)
cols <- brewer.pal(11, "RdYlGn")

par(oma=c(0,0,0,0), mar=c(0,0,2,0))
symbols(1, thermometers = cbind(.5, 1, y/z), fg = cols[round(y/z*10)], inches=3.5, 
        xlab = NA, ylab = NA, yaxt='n', xaxt='n', bty='n',  
        main = paste("Funds raised as of", format(Sys.Date(), "%m-%d-%y")))
text(1, y=1.4, paste0("$", y, "/", z))
text(1, y=.8, paste0(y/z*100, "%"),  offset = 3)
```


### Swag, giveaways, Prizes!!!

Pens, note pads, USB drives, buttons... Students love these and they help make the event fun. If we get something special, we can give it away in a ``midnight raffle" to help keep the energy level high.

### Donate a Meal
Students can only work on this data while on site, so feeding them is critical! If you can't donate dollars directly, consider sponsoring a meal or snacks for a day. 


### Participate as a Consultant

Spend an hour or two getting to know the students and offering your sage advice. 
This is an excellent recruiting opportunity; you get to watch students working in teams, under pressure, striving to understand possibly the most complex data set they have encountered. 
At other institutions, students have received internships and interviews that have led to full-time employment. 
Success at DataFest requires that a team have a combination of computational, statistical, and human skills, as well as the ability to communicate clearly and extremely concisely.

[[Register here]](https://goo.gl/forms/vvGg3NegVX0qqTvf2) to sign up as a roaming consultant. 

### Contact 

Contact Robin Donatello, rdonatello@csuchico.edu for more information on how your organization can help create a memorable weekend. 

